---
title: "Hamilton_Project"
output: 
  html_document: 
    keep_md: yes
---

#Introduction
Below, I will describe the process I chose for using the Randow Forest
machine learning techique for predicting the class variable in this dataset

##Step 1: Data Cleaning and remove unuseable attributes

The first step is to load the data and remove all of the NA values in the 
dataset. Next, I removed the attributes that aren't useful in the prediction.
These variables for removal are x, user_name, raw_timestamp_part 1 and 2, cvtd_timestamp
new_window, and num_window.

```{r}
library(caret)
library(e1071)
library(rattle)
library(rpart)

#load data
traindata <- read.csv("pml-training.csv", header=T, na.strings=c("NA", "#DIV/0!"))
testdata <- read.csv("pml-testing.csv", header=T, na.string=c("NA", "#DIV/0!"))

#remove nas

traindata_NARemoved<-traindata[, apply(traindata, 2, function(x) !any(is.na(x)))]
testdata_NARemoved<-testdata[, apply(testdata, 2, function(x) !any(is.na(x)))]

#Remove features that will not be used for feature detection
finaltrainingdata <- traindata_NARemoved[,-c(1:7)]
finaltestdata <- testdata_NARemoved[,-c(1:7)]
```

##Step 2: Model Setup
During this step, I partitioned the data with 75% for training and 25% for testing.
I used the K-folds technique to cross valid my data set by creating 10 folds. Lastly
I ran the Random Forest on the training set.

```{R ModelRun, cache=TRUE}
#Split training set in training and test set and ran Random forest algorthim 
#The cross vaildation technique was used was K-Folds in which I create 10
#of them.
inTrain<-createDataPartition(y=finaltrainingdata$classe, p=0.75,list=F)
training<-finaltrainingdata[inTrain,] 
test<-finaltrainingdata[-inTrain,] 
set.seed(1)
FoldsSplit <-trainControl(method="cv", number=10, allowParallel=T, verbose=T)
ModFit <-train(classe~.,data=training, method="rf", trControl=FoldsSplit, verbose=F)
```

##Step 3: Results 
The model has an accuracy of 99% in prediction rate of the test set. Also, I 
ran the model against the test case for the quiz and it was 100% correct.

``` {r}
#Prediction Results
predResults<-predict(ModFit, newdata=test)
confusionMatrix(predResults, test$classe)

#prediction against test cases
testcaseResults <- predict(ModFit, newdata = finaltestdata)
testcaseResults

```

